Manuscript title here

### 2021-06-06 doc/ms/ms.Rmd
updated skew temp figures

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in community energy fluxes. The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean") %>% round(2)` (`r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5") %>% round(2)` -- `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5") %>% round(2)`) to `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`). Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`). The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure SX), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX). This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.

@@

Changing global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide. Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities. Further, within consumer communities energy fluxes are skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and smaller

>>>>

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in community energy fluxes. The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean") %>% round(2)` (`r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5") %>% round(2)` -- `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5") %>% round(2)`) to `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`). Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`). The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure S5), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX). This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.

@@

Changing global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide. Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities, as predicted. Further, within consumer communities energy fluxes were skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and towards smaller, quick turnover populations at warmer temperatures. The organization of energy fluxes became less likely due to random chance moving from cooler to warmer temperatures, but this trend reversed at the warmest temperatures. The tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests higher population biomass turnover may be selected f temperatures .

### 2021-06-06 doc/ms/tables-figures.Rmd
updated skew temp figures

>>>>

Figure 5. Non-random organization of community energy fluxes in relation to population biomass turnover (*P:B*) with mean annual temperature ($^\circ$C). Non-random organization is measured by the proportion of randomly generated skew statistics, $Sk_{flux}$, of equal or greater value. Observing an empirical value of $Sk_{flux}$ with a low probability of occurrence by random chance suggests non-random organization of community energy fluxes.

```{r echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(temperature_skew_fig)
grid.draw(pb_probs_plot)
```
